Simulation Study: Varying Informativeness (smooth)

### 2018-08-31 datasets/simulations/simulations-varyinginformativeness-smooth.Rmd
Plot informativeness functions; try smooth informativeness

---
title: "Simulation Study: Varying Informativeness"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with varying levels of informativeness of an informative covariate. The
covariate is sampled uniformly from the interval [0, 1], and the conditional
probability of a test being non-null is a step function of the covariate with
two levels (over the intervals [0, 4/5], (4/5, 1]) where the size of the step
is used to indicate the informativeness of the covariate.

For all settings, the marginal proportion of null hypotheses is set to 80%.
A tuning parameter is used to modify the informativeness of the covariate
such that 0 corresponds to an uninformative covariate, and 1 corresponds to a
fully informative covariate (i.e. all tests with covariate values in [0, 4/5]
are null and all tests in (4/5, 1] are non-null).

@@

@@

```{r info00-parameters}
pi0 <- pi0_varyinfo80(0.00)             # numeric: proportion of null hypotheses
seed <- 1010
```

@@

```{r info20-parameters}
pi0 <- pi0_varyinfo80(0.20)             # numeric: proportion of null hypotheses
seed <- 1201
```

@@

```{r info40-parameters}
pi0 <- pi0_varyinfo80(0.40)             # numeric: proportion of null hypotheses
seed <- 51
```

@@

```{r info60-parameters}
pi0 <- pi0_varyinfo80(0.60)             # numeric: proportion of null hypotheses
seed <- 500
```

@@

```{r info80-parameters}
pi0 <- pi0_varyinfo80(0.80)             # numeric: proportion of null hypotheses
seed <- 608
```

@@

```{r info100-parameters}
pi0 <- pi0_varyinfo80(1.00)             # numeric: proportion of null hypotheses
seed <- 808
```

>>>>

---
title: "Simulation Study: Varying Informativeness (smooth)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with varying levels of informativeness of an informative covariate. The
covariate is sampled uniformly from the interval [0, 1], and the conditional
probability of a test being non-null is a smooth function of the covariate taking
values between 0 and 1 based on the logistic function.

For all settings, the marginal proportion of null hypotheses is set to 80%.
A tuning parameter is used to modify the informativeness of the covariate
such that 0 corresponds to a completely uninformative covariate, and increasing
"informativeness" corresponds to more non-null tests concentrating in a smaller
range of the covariate. The functional relationship between the covariate and
the null probability over varying informativeness is shown below.

@@

First, we show the form of the relationship between the informative covariate and null
proportion, pi0, across varying levels of "informativeness."

```{r plot-informativeness, fig.width = 9, fig.height = 2.5}
xseq <- seq(0, 1, by = .01)
pi0trends <- lapply(seq(0, 1, by = .2), function(i) {
    tibble(info = i, x = xseq,
           pi0 = pi0_varyinfo80l(i)(xseq))
})
pi0trends <- bind_rows(pi0trends)

ggplot(pi0trends, aes(x = x, y = pi0)) +
    geom_line() +
    geom_text(aes(label = round(pi0, 3), hjust = x, vjust = round(pi0)),
              dplyr::filter(pi0trends, x == 0 | x == 1),
              size = 3, color = 'blue') + 
    theme_bw() +
    scale_x_continuous("x (informative covariate)", breaks = 0:1) +
    scale_y_continuous(labels = scales::percent) +
    facet_grid(. ~ info, labeller = label_both) +
    ggtitle("Covariate vs. pi0 for varying informativeness")
```

@@

```{r info00-parameters}
pi0 <- pi0_varyinfo80l(0.00)             # numeric: proportion of null hypotheses
seed <- 1010
```

@@

```{r info20-parameters}
pi0 <- pi0_varyinfo80l(0.20)             # numeric: proportion of null hypotheses
seed <- 1201
```

@@

```{r info40-parameters}
pi0 <- pi0_varyinfo80l(0.40)             # numeric: proportion of null hypotheses
seed <- 51
```

@@

```{r info60-parameters}
pi0 <- pi0_varyinfo80l(0.60)             # numeric: proportion of null hypotheses
seed <- 500
```

@@

```{r info80-parameters}
pi0 <- pi0_varyinfo80l(0.80)             # numeric: proportion of null hypotheses
seed <- 608
```

@@

```{r info100-parameters}
pi0 <- pi0_varyinfo80l(1.00)             # numeric: proportion of null hypotheses
seed <- 808
```
